Ideal model selection is impossible

### 2014-11-24 Facticity/Facticity/paper.tex

>>>>

Adriaans takes this problem seriously and attempts to address it by imposing additional restrictions on the ordering of TMs implied by the used UTM \cite{adriaans2012facticity}. We are skeptical that such measures can effectively eliminate this problem without resorting to orderings of the TMs that are not admissible [TODO ref].
